Automated Topic Naming

### 2011-09-05 ese/ese.tex
expand on why postgresql performs soo poorly?

%\todo{update these numbers but from where? }
% 0.177215189873 / 6
% .02953586497883333333
% (0.0298507462687 + 0.0661157024793 + 0.0634920634921 + 0 + 0.115384615385) / 6
% .04580718793751666666

@@

Figure \ref{fig:best-learn-per-tag} shows that MaxDB and MySQL have quite different results, as the ROC values for \emph{reliability} and \emph{functionality}
 swap between projects. For PostgreSQL, the performance is nearly always poorer than the other two systems. 
\todo{expand on why?}

>>>>

%\DONE{update these numbers but from where? }
% 0.177215189873 / 6
% .02953586497883333333
% (0.0298507462687 + 0.0661157024793 + 0.0634920634921 + 0 + 0.115384615385) / 6
% .04580718793751666666

@@

Figure \ref{fig:best-learn-per-tag} shows that MaxDB and MySQL have
quite different results, as the ROC values for \emph{reliability} and
\emph{functionality} swap between projects. For PostgreSQL, the
performance is nearly always more poor than the other two systems. The
reason for this lack of performance could be that the number of
topics, $N$ could be non-optimal for PostgreSQL. Perhaps topics were
getting too mixed and it was becoming hard to distinguish one topic
from the next. PostgreSQL's dataset was the largest of the 3 projects,
the XML data-dump that described the PostgreSQL topics that we
annotated was 8X larger than MySQL and 1.7X larger than MaxDB. These
size differences arise from the number of commits, the number of files
and the verbosity of the commit descriptions.

%\DONE{expand on why?}
